Separating random and deterministic sources of computational noise in explore-exploit decisions

### 2024-05-17 manuscript/2024 - Plot Comp Bio/manuscript_DeterministicRandomNoise.tex
ethics statement

\begin{figure}[H]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/RDBayes_ratio__paironly.jpg}
	\caption{(A) Model based analysis showing the posterior distributions over the ratio of the group-level mean of the standard deviations of  random and deterministic noise between horizon 6 and horizon 1 respectivelly. The ratios in the standard deviations of noises between horizon 6 and horizon 1 are similar for random and deterministic noise.}
	\label{fig:ratio}
\end{center}
\end{figure}

@@

\section*{Materials and Methods}
\subsection*{Participants}

80 participants (ages 18-25, 37 male, 43 female) from the University of Arizona undergraduate subject pool participated in the experiment. 15 were excluded on the basis of performance, using the same exclusion criterion as in \cite{wilson2014}. In this exclusion criteria, we measured the accuracy of each participant's choices by calculating the percentage of times that a participant chose the bandit with the higher underlying mean payouts in the last choice of a long horizon game, intuitively people should figure out which bandit has a higher mean payout by the last trial and should have an accuracy measure significantly above 50\%, specifically, we computed the likelihood that the measured accuracy can be achieved by making a completely random choice between the two options and excluded participants with a likelihood greater than 0.1\%, in other words, participants who didn't show an accuracy significant above chance with $p < 0.001$ were excluded in the analysis. This left 65 for the main analysis. Note that including the 15 badly performing subjects did not change the main results (Supplementary Figures S1, S2, S11)

>>>>

\begin{figure}[H]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/RDBayes_ratio.jpg}
	\caption{Model based analysis showing the posterior distributions over the ratio of the group-level mean of the standard deviations of  random and deterministic noise between horizon 6 and horizon 1 respectivelly. The ratios in the standard deviations of noises between horizon 6 and horizon 1 are similar for random and deterministic noise.}
	\label{fig:ratio}
\end{center}
\end{figure}

@@

\section*{Materials and Methods}
\subsection*{Ethics Statement}
Human subject protocols were approved by the University of Arizona institutional review board (IRB \# 1411567117). Written informed consent was given by all participants prior to participating in the study.

\subsection*{Participants}
80 participants (ages 18-25, 37 male, 43 female) from the University of Arizona undergraduate subject pool participated in the experiment. 15 were excluded on the basis of performance, using the same exclusion criterion as in \cite{wilson2014}. In this exclusion criteria, we measured the accuracy of each participant's choices by calculating the percentage of times that a participant chose the bandit with the higher underlying mean payouts in the last choice of a long horizon game, intuitively people should figure out which bandit has a higher mean payout by the last trial and should have an accuracy measure significantly above 50\%, specifically, we computed the likelihood that the measured accuracy can be achieved by making a completely random choice between the two options and excluded participants with a likelihood greater than 0.1\%, in other words, participants who didn't show an accuracy significant above chance with $p < 0.001$ were excluded in the analysis. This left 65 for the main analysis. Note that including the 15 badly performing subjects did not change the main results (Supplementary Figures S1, S2, S11)
